Aldebaran~b's temperate past uncovered in planet search data

### 2018-08-08 ref1/response.txt

Response to Reviewer's Comments:

First, we thank the referee for their report; we also apologize for the delay in
response.  We will address the comments of the referee in-line below.  In
addition to the changes discussed below we have modified the acknowledgements
section to add several new acknowledgements.

> Reviewer's Comments:

> This is an interesting paper and a clever use of statistical techniques to use
> historical data. I would like a few comments addressed and some revisions made
> before I recommend publication.

> I do find the title somewhat over the top given the uncertainties in Fig. 6! To
> me the paper is more about applying a novel (to astronomers!) statistical method
> to measure parameters that we otherwise would not be able to. [Ed: A little over
> the top is OK for an ApJL title... ]

We have not changed the title.

> Comments and concerns:

> (1) Since Kepler is mentioned so prominently in the abstract, SONG should be
> too, and judging by Fig 1, TLS may be worth a mention too.

We have done this; we now mention SONG in the abstract.  We have left TLS out of
the abstract since the archival data we use come only partially from TLS.

> (2) Discussion of the scaling relations: Given that there is work that shows
> that there might be a mean-molecular weight term in the numax scaling relation,
> a discussion of that and the reference to the paper to be given. This is
> relevant both after Eq. 3 and Eq. C7.

We have added two sentences with one reference addressing this point, in the
paragraph following Eq. (3).

> (3) I understand that the statistical method used has the acronym CARMA,
> however, for most astronomers CARMA is a radio array (Combined Array for
> Research in Millimeter-wave Astronomy). The caption of Fig 4 was thus very
> confusing when I first read it (I, like many others, look at figures before
> reading), and for a few moments I thought we could use radio observations to
> study pulsations. Please change that to Something like "Power spectral density
> derived from the CARMA analysis ..."

Done.

> (4) Were the same set of stellar models used for calculating Aldebaran's
> properties using PARAM and the results in Fig 6? The text is not clear about
> this and for consistent results, the same models should be used.

Originally a separate set of models were used; now the same MESA models are used
for both the PARAM code and the insolation calculation.  This is explicitly
mentioned in the text (paragraph beginning "With the determination of the
stellar mass...").

> (5) The medalist scale of the models is not mentioned in Section C.1. I.e., what
> solar metallicity and abundance mixture was assumed? Grevesse & Sauval (1998),
> Asplund et al. (2009)? Please specify. The difference is enough to cause a large
> effective change in Z/X and hence deduced stellar properties.

We now state the medalist scale explicitly, with reference to Grevesse & Noels
(1993), from which it is derived and Rodrigues, et al. (2017) which describes
its use.  (First bullet point of C.1.)

> (6) There are other (non-seismic) works that deal with modelling Aldebaran
> (e.g., Abia et al. 2012). How do the results obtained in this paper compare with
> literature values?

We have added a sentence in Section 4.4 pointing to Abia+2012 and noting that
our non-asteroseismic mass value and uncertainty are consistent with that work.
The asteroseismic mass estimate is, of course, improved in uncertainty but
remains consistent.

> (7) Massarotti et al. are not the only ones who report a low metallicity for
> Aldebaran, Liu et al. 2017 report [Fe/H]=-0.27. Sharma et al. (2016) claim
> -0.16. The choice of values in Table~2 should therefore be justified.

The referee is correct that there is a large scatter in the reported metallicity
results for Aldebaran. The focus of this work is the new analysis of historical
RV data and how this allows new inference. The treatment this scatter of, or at
least justification of the selected metallicity, is beyond the scope of this
work. In the text we already indicate that there is a large scatter and hence we
select a number of metallicity values. While we agree there is little science
behind this selection it is still broadly representative and should allow
readers to interpret the impact of metallicity.

--------
Data Editor's comments:

The authors should provide the RV data shown in Figure 3 as Data behind the
Figure (DbF). The readers would surely appreciate having this important data set
available with the published article.

### 2018-08-16 paper/aldebaran.tex

We have used the additional constraint of \numax determined from this analysis
to update the stellar properties of Aldebaran.  The details of the stellar
modelling are presented in Appendix \ref{sec:mod}.  We have considered the
impact of our additional \numax constraint and run our analysis for different
sets of spectroscopic estimates.  For final values we adopt the
\citet{2012Sheffield} spectroscopic solution as being `middle of the road'
estimates.  For the analysis without constraint on \numax we find estimates of
the stellar properties as $M = 1.27^{+0.24}_{-0.20} \, \mathrm{M_{\odot}}$ and
age $4.9^{+3.6}_{-2.0} \, \rm Gyr$.  With the inclusion of \numax we find $M =
1.16\, \pm \, {0.07} \, \mathrm{M_{\odot}}$ and age $6.4^{+1.4}_{-1.1} \, \rm
Gyr$.  It is clear that the addition of \numax provides substantially more
precise estimates of mass and age. With this stellar mass, the radial velocity
signal translates to an inclination-dependent planetary mass of $M\,\sin\,{i} =
5.8 \pm 0.7~M_J$ \citep[Equation~1]{Torres2008}, a massive giant planet; for
sufficiently high inclinations ($\gtrsim 45^\circ$), the mass of Aldebaran~b may
exceed $13~M_J$, making it a possible low-mass brown dwarf candidate. A recent
study by \citet{2018arXiv180105239H} has cast doubt on the validity of the
detection of the massive planet $\gamma$~Draconis~b, and by extension similar
planets around similar K~giants such as Aldebaran. We remain convinced that the
$\gamma$~Draconis problem is not an issue in this case, and Aldebaran~b is a
bona fide planet, for reasons outlined in Appendix~\ref{gamma_dra}.

@@

We would like to thank Tim Bedding, David Hogg and Dan Foreman-Mackey for their helpful discussions.

>>>>

We have used the additional constraint of \numax determined from this analysis
to update the stellar properties of Aldebaran.  The details of the stellar
modelling are presented in Appendix \ref{sec:mod}.  We have considered the
impact of our additional \numax constraint and run our analysis for different
sets of spectroscopic estimates.  For final values we adopt the
\citet{2012Sheffield} spectroscopic solution as being `middle of the road'
estimates.  For the analysis without constraint on \numax we find estimates of
the stellar properties as $M = 1.27^{+0.24}_{-0.20} \, \mathrm{M_{\odot}}$ and
age $4.9^{+3.6}_{-2.0} \, \rm Gyr$.  This value and uncertainty are consistent
with those obtained from other non-asteroseismic analyses of Aldebaran
\cite[e.g.][]{Abia2012,Hatzes2015}. With the inclusion of \numax we find $M = 1.16\, \pm
\, {0.07} \, \mathrm{M_{\odot}}$ and age $6.4^{+1.4}_{-1.1} \, \rm Gyr$.  It is
clear that the addition of \numax provides substantially more precise estimates
of mass and age. With this stellar mass, the radial velocity signal translates
to an inclination-dependent planetary mass of $M\,\sin\,{i} = 5.8 \pm 0.7~M_J$
\citep[Equation~1]{Torres2008}, a massive giant planet; for sufficiently high
inclinations ($\gtrsim 45^\circ$), the mass of Aldebaran~b may exceed $13~M_J$,
making it a possible low-mass brown dwarf candidate. A recent study by
\citet{2018arXiv180105239H} has cast doubt on the validity of the detection of
the massive planet $\gamma$~Draconis~b, and by extension similar planets around
similar K~giants such as Aldebaran. We remain convinced that the
$\gamma$~Draconis problem is not an issue in this case, and Aldebaran~b is a
bona fide planet, for reasons outlined in Appendix~\ref{gamma_dra}.

@@

We would like to thank Tim Bedding, David Hogg and Dan Foreman-Mackey for their
helpful discussions.  We would like to thank the anonymous referee for their
efforts and their comments.
